Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-11 ms.tex
analytic temperature.

Continuity of the entropy derivative at the stagnation radius where $v = 0$ requires that the temperature at this location be given by (eq.~[\ref{eq:first_law}])
\begin{align}
T|_{r_{s}}& = \frac{\gamma-1}{\gamma}\frac{\mu m_p
  \tilde{v}_{w}^{2}}{2k} \approx \frac{2}{5} \frac{7-2\nu}{7} \frac{\mu m_p
   v_{w}^{2}}{2k}\nonumber\\ 
 &\approx
 \begin{cases}
  4.5\times 10^6\ \, v_{500}^2 \,\,{\rm K} & \text{core} \\
  5.3\times 10^6\ \, v_{500}^2 \,\,{\rm K} & \text{cusp},
 \end{cases}
\label{eq:Tanalytic}
\end{align}
where we have assumed $\gamma=5/3$, $v_{500} \equiv v_{w}/(500$ km
s$^{-1}$) and $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm
    s}}$ is the density power-law slope at $r = r_{\rm s}$.
Empirically, we find that
\begin{align}
\densSlope \simeq \frac{1}{6} \left(4 \Gamma+3\right).
\label{eq:densSlope}
\end{align}

@@

Perhaps a more readily addressable test is whether a steady-state accretion
picture can account for the the large scatter, typically of $2-3$ orders of magnitude, in $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter could result from at 
least three effects: (1) instric scatter in the scaling relationships ($\Mbh-\sigma$ and $\Mbh-L_{\rm
  bulge}$) used to measure $\Mbh$; (2) the strong sensitivity of the accretion rate to
the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  When 
combined with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Appendix \ref{fig:NickPlot2}), this can lead to order of magnitude differences in $\dot{M}$; (3) differences angular momentum of the infalling gas from galaxy to galaxy, resulting in differences in the fraction of the gas lost to outflows, $\Mbh$.  Also potentially contributing is the order of magnitude difference, at fixed $v_w$ and $M_{\bullet}$, between $\dot{M}$ for core and cusp galaxies (Fig.~\ref{fig:bh_growth}).  Differences in $\dot{M}$ are augmented by the expectation that $L_{\rm X} \propto \dot{M}^{2} $ for radiatively inefficient flows.

>>>>

Continuity of the entropy derivative at the stagnation radius where $v = 0$ requires that the temperature at this location be given by (eq.~[\ref{eq:first_law}])
\begin{align}
T|_{r_{s}}& = \frac{\gamma-1}{\gamma}\frac{\mu m_p
  \tilde{v}_{w}^{2}}{2k} \approx \frac{2}{5} \frac{7}{7-2\nu} \frac{\mu m_p
   v_{w}^{2}}{2k}\nonumber\\ 
 &\approx
 \begin{cases}
  4.5\times 10^6\ \, v_{500}^2 \,\,{\rm K} & \text{core} \\
  5.3\times 10^6\ \, v_{500}^2 \,\,{\rm K} & \text{cusp},
 \end{cases}
\label{eq:Tanalytic}
\end{align}
where we have assumed $\gamma=5/3$, $v_{500} \equiv v_{w}/(500$ km
s$^{-1}$) and $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm
    s}}$ is the density power-law slope at $r = r_{\rm s}$.
Empirically, we find that
\begin{align}
\densSlope \simeq \frac{1}{6} \left(4 \Gamma+3\right).
\label{eq:densSlope}
\end{align}

@@

Perhaps a more readily addressable test is whether a steady-state accretion
picture can account for the the large scatter, typically of $2-3$ orders of magnitude, in $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter could result from at 
least three effects: (1) instric scatter in the scaling relationships ($\Mbh-\sigma$ and $\Mbh-L_{\rm
  bulge}$) used to measure $\Mbh$; (2) the strong sensitivity of the accretion rate to
the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  When 
combined with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Appendix
\ref{fig:NickPlot2}), this can lead to order of magnitude differences
in $\dot{M}$; (3) differences angular momentum of the infalling gas
from galaxy to galaxy, resulting in differences in the fraction of the
gas lost to outflows, $\Mbh$.  Also potentially contributing is the
order of magnitude difference, at fixed $v_w$ and $M_{\bullet}$,
between $\dot{M}$ for core and cusp galaxies
(Fig.~\ref{fig:bh_growth}).  Differences in $\dot{M}$ are augmented by
the expectation that $L_{\rm X} \propto \dot{M}^{2} $ for radiatively
inefficient flows {\bf AG: Don't forget differences in eta}.
